High-resolution ALMA observations of V4046\,Sgr: a circumbinary disc with a thin ring

### 2020-12-04 Draft_V4046_Sgr_mnras.tex
Add files via upload

% Only include extra packages if you really need them. Common packages are:
\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
%% \usepackage{amssymb}	% Extra maths symbols

@@

% Abstract of the paper
\begin{abstract}
  The nearby V4046\,Sgr spectroscopic binary hosts a gas-rich disc known for its wide cavity and dusty ring.  We present high resolution ($\sim$20--50\,mas) ALMA observations of the 1.3\,mm  continuum which, combined with SPHERE-IRDIS polarized images and a well-sampled spectral energy distribution (SED), allow us to propose a physical model for the source using radiative transfer (RT) predictions. The new ALMA data reveal a very thin ring at a radius of 13.32$\pm$0.26\,au (Ring13), with a marginally resolved radial width of 1.50$\pm$0.72\,au. Ring13 is surrounded by a $\sim$10\,au-wide gap, and it is flanked by a very mm-bright outer ring (Ring24) with a sharp inner edge at 24\,au. The steeply decreasing brightness of Ring24 breaks at $\sim$35\,au into a shallow tail. In order to reproduce the SED, the model that we propose requires an inner ring at $\sim$6\,au (Ring6) in small dust grains, hiding under the IRDIS coronagraph, and that surrounds an inner circumbinary disc. Faint mm-continuum close ($\sim0\farcs02 $ ****GIVE ERRORS***) to the stellar position is picked up by ALMA. The surprisingly thin Ring13 is nonetheless roughly 5 times wider than the model scale height, and could thus be long-lived. The strong near-far disc asymmetry at 1.65\,$\micron$ points at a very forward-scattering phase function, and requires grain radii of no less than 0.4\,$\micron$. The previously reported scattered-light shadow of the secondary star is also reproduced by the RADMC3D RT package. 
\end{abstract}

@@

V4046\,Sgr was observed in differential polarization imaging (DPI) mode with SPHERE/IRDIS on March 13, 2016 \citep[see][for details]{Avenhaus_2018}. Here we use a new reduction of the $H$ band data produced with the IRDAP pipeline \citep{2020A&A...633A..64V}, which can separate stellar and instrumental polarization. The polarized signal is consistent with the previous image in \citet{Avenhaus_2018}. The degree of linear polarization of the central and unresolved signal in V4046\,Sgr is only 0.13\%, with a systematic uncertainty of 0.05\% due to time-varying atmospheric conditions during the exposures. The angle of polarization is aligned with the disc major axis, as expected given that the target has Av=0.0 \citep{2016ApJ...828...69M} and the entire polarization is dominated by circumstellar rather than inter-stellar material.

@@

The resulting {\tt uvmem} image shown in Fig.~\ref{fig:images_vs_simulated} exhibits previously unseen substructure of the disc. This image reveals that the disc features two rings of large dust grains with a broad gap between them, i.e. Ring13 at 13\,au and Ring24 starting at 24\,au. The wide and bright Ring24 reaches its peak intensity at $\sim$30\,au, beyond which it drops steeply before breaking at $\sim$35\,au into a shallow tail. While this is the first observation of Ring13, \citet{Ru_z_Rodr_guez_2019} did anticipate its existence as their ALMA continuum image showed a distinct excess between $\sim$10 and 17\,au.

\begin{figure*}
  \includegraphics[width=\textwidth]{hot_two_E.pdf}
  \caption{Comparison of observations and simulated images at 1.65\,$\micron$ and 1.3 mm continuum of the circumbinary disc orbiting V4046\,Sgr. From top to bottom: DPI image and ALMA Band 6 observations; simulated images of the parametric model. Top left panel: SPHERE-IRDIS \textit{H}-band image with a yellow filled circle that represents the N\_ALC\_YJH\_S coronagraph with a radius of $\sim0\farcs12$, or $\sim$8.6\,au at 72.4\,pc. Top right panel: 1.3\,mm continuum {\tt uvmem} model image. The yellow ellipse shows the size of the natural-weighted beam ($ 0\farcs062 \, \times \, 0\farcs055$), and the small orange ellipse shows an estimated {\tt uvmem} beam size ($\sim0\farcs035 \, \times \, \sim0\farcs031$). The inset zooms into the central emission, and the green star marks the star positions. Bottom left panel: synthetic image at 1.65\,$\upmu m$. Bottom right panel: synthetic image at 1.3\,mm. . For all the images in the figure the colour scale is linear.}
  \label{fig:images_vs_simulated}
\end{figure*}

@@

Interestingly, the ALMA image also detects faint 1.3\,mm continuum emission near the stellar positions (See the inset in Fig.~\ref{fig:images_vs_simulated}). Since this faint central emission is larger than the angular resolution, it is probably stemming from thermal emission from  large dust grains rather directly from the stars. The main blob of this dust structure is at a estimate distance of only $0\farcs012\pm0\farcs002$, or $\sim$0.9\,au from the binary system, and may be part of inner disc introduced in the RT model to match the SED (see Sec.~\ref{sec:model} below).

@@

The scattered-light image shown in Fig.~\ref{fig:images_vs_simulated} also shows a double ring structure in the micron-sized dust distribution. The observed morphology presents an inner cavity of $\sim$10\,au in radius and two rings located at 14.10$\pm$0.01, coincident with Ring13, and 24.62$\pm$0.08\,au, coincident with Ring24, with a small gap between them at $\sim$20\,au. The observed second ring matches the inner wall of the 1.3\,mm continuum emission outer ring \citep{Ru_z_Rodr_guez_2019}. Two other important features that are present in the image are: the brightness asymmetry and the shadows projected on the disc produced by the close binary system as they eclipse each other, discovered by \citet{dOrazi}.

@@

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{SED_.png}
    \caption{The observed SED of V4046\,Sgr (black points and solid red curve) compared with the model (blue). The black points represent the measured photometry and the red line shows an archival \textit{Spitzer} IRS spectrum. The dashed silver curve shows the emission of the stellar photosphere model.}
    \label{fig:SED}
\end{figure}

@@

The stars were modeled using two Kurucz photospheres models \citep{1979ApJS...40....1K, 1997A&A...318..841C}, with T$_{\mathrm{eff},1} =$ 4350\,K, R$_{*,1} =$ 1.064\,R$_{\sun}$, M$_{*,1} =$ 0.90\,M$_{\sun}$ and T$_{\mathrm{eff},2} =$ 4060\,K, R$_{*,2} =$ 1.033\,R$_{\sun}$, M$_{*,2} =$ 0.85\,M$_{\sun}$ respectively and with an accretion rate of $\mathrm{log}(\,\dot{\mathrm{M}/(\mathrm{M}_{\sun}\,\mathrm{yr^{-1}})}) = -$9.3 for both cases to include excess UV due to stellar accretion \citep{10.1111/j.1365-2966.2011.19366.x}. The stars were placed at a mutual separation of 0.041\,au, so that their centre of mass coincides with the origin, and oriented at a PA of 250\,$\degr$, so that the secondary lies to the NWW from the primary, thus casting the same shadow as observed by \citet{dOrazi}.

Reproducing the radial and vertical structure of the V4046\,Sgr disc turned out to be challenging. We built the model in terms of the gas distribution, and with two different dust populations: larger grains that are vertically settled and dominate the total dust mass, and a population of smaller grains that are uniformly mixed with the gas and reach larger heights above the mid-plane.

Assuming a three dimensional model in a cylindrical reference frame with coordinates ($r$, $\theta$, $z$), the gas density ($\rho_{\mathrm{gas}}$) distribution follows
\begin{equation}
  \rho_{\mathrm{gas}}(r,z) =\frac{\Sigma_{\mathrm{gas}}(r)}{\sqrt{2\pi} \, H(r)} \mathrm{exp}\left[-\frac{1}{2} \left(\frac{z}{H(r)}\right)^2\right],
\end{equation}
where $H(r)$ is the scale height profile and $\Sigma_{\mathrm{gas}}(r)$ is the gas surface density profile.

The parametric scale height profiles for the gas and for each dust population are 
\begin{equation}
    \label{scale}
  H(r)=\chi \, H_{\circ} \, [r/r_{\circ}]^{\psi(r)},
\end{equation}
where $H_\circ$ is the scale height at r = $r_\circ$, $\psi$ is the flaring index and $\chi$ is a scaling factor (in the range $0-1$) that mimics dust settling. The gas and the small dust grains have no settling, so $\chi_{gas}$ = 1. The radial spread of Ring13 appears about five times wider in the gas-tracing NIR observations than in the fluxes received from larger grains with ALMA. We assume that the same ratio holds in the vertical direction (due to the settling of larger grains towards the disk's midplane), leading to $\chi_{ld}=1/5$.

For the vertical structure, \citet{dOrazi} found flaring angles of $\varphi$ = 6.2$\pm$0.6\,$\degr$ for the inner ring and $\varphi$ = 8.5$\pm$1.0\,$\degr$ for the outer one. Our model uses the same values, with two different flaring indexes $\psi$. The separation between the two values were set at $r$ = 18\,au with $\psi=0.15$ for Ring6 and Ring13, and $\psi=0.5$ for Ring24. The scale height is $H_\circ = 0.45$\,au at $r_\circ = 18$\,au.

We propose a three ringed structure, so we defined the total gas surface density by a combination of four individual components: the inner disc, Ring6, Ring13 and Ring24. The total gas surface density is then  given  by:
\begin{equation}
  \Sigma_{\mathrm{gas}}(r) = \Sigma_{\mathrm{inner\,disc}} + \Sigma_{\mathrm{Ring6}} + \Sigma_{\mathrm{Ring13}} + \Sigma_{\mathrm{Ring24}}
\end{equation}

The inner disc follows a power law function defined by
\begin{equation}
  \Sigma_{\mathrm{inner\,disc}}(r) =\Sigma_\mathrm{c} \left(\frac{r}{R_\mathrm{c}}\right)^{-\gamma}  \, \mathrm{exp}\left[-\left(\frac{r}{R_\mathrm{c}}\right)^{2-\gamma}\right],
\end{equation}
where $R_c$ is a characteristic radius and $\gamma$ is the surface density gradient. We used $R_c$ = 16\,au, $\Sigma_\mathrm{c} =2.7\times10^{-4}$ and a fixed $\gamma$ = 1 as it is a typical value for discs \citep{Andrews_2009,Andrews_2010}. The gas surface density begin at 0.3\,au, out of the zone expected to be cleared by dynamical interactions with the central binary \citep{Art_Lu}, which is expected to be $\sim$0.2\,au.

We chose to use Gaussian profiles to parameterize Ring6 and Ring13,
\begin{equation}
  \Sigma_{\mathrm{Ring}}(r) = \frac{\Sigma_\circ}{\sqrt{2 \pi} \sigma}
  \, \mathrm{exp}\left[-\frac{1}{2}\left(\frac{r-\mu}{\sigma}\right)^{2}\right],
\end{equation}
where we define constants that correspond to the centroid radii \{$\mu_{\mathrm{Ring6}}=5.5$\,au, $\mu_{\mathrm{Ring13}}=15$\,au\}, ring widths \{$\sigma_{\mathrm{Ring6}}=1$\,au, $\sigma_{\mathrm{Ring13}}=2.05$\,au\}, and normalizations \{ $\Sigma_{\circ,\mathrm{Ring6}}=8\times10^{12}$, $\Sigma_{\circ,\mathrm{Ring13}}=4.2\times10^{13}$\} for both components separately.

For Ring24 we used the same power law than the inner disc but scaled by a $\delta_{\mathrm{sd}}$ factor:
\begin{equation}
  \Sigma_{\mathrm{Ring24}} = \Sigma_{\mathrm{inner\,disc}}(r)\, \delta_{\mathrm{sd}},
\end{equation}
with $\delta_{\mathrm{sd}}$ = 5.3$\times 10^4$. But the inner wall of Ring24 follows a different behaviour. Between $R_\mathrm{in}$ and $R_\mathrm{peak}$, which respectively mark  the beginning and the maximum density peak of the outer ring, the gas density profile is multiplied by an additional factor
\begin{equation}
    \epsilon(r) = \left(\frac{ r - R_\mathrm{in}}{R_\mathrm{peak} - R_\mathrm{in}}\right)^3.
\end{equation}
This parameter allow us to model a smoother inner wall of the outer ring, with $R_\mathrm{in,gas}$ = 18.\,au and $R_\mathrm{peak,gas}$ = 26.8\,au. This factor is also applied to the large dust population with $R_\mathrm{in,ld}$ = 24.7\,au and $R_\mathrm{peak,ld} = R_\mathrm{peak,gas}$.

@@

Since the large dust grains are less coupled to the gas, their distribution has some important differences that require a special parameterisation, with a large inner cavity, a larger gap between the rings and a break in the outer ring. We also truncated the model large-grain density at 64\,au. The large-dust surface density profile is defined by the sum of its two components
\begin{equation}
  \Sigma_{\mathrm{ld}}(r) = 
  \Sigma_{\mathrm{Ring13,ld}} + \Sigma_{\mathrm{Ring24,ld}}.
\end{equation}

For the inner ring, we chose a Gaussian profile parameterized with centroid radius $\mu_{\mathrm{Ring13, ld}}=13.38$\,au, ring width of $\sigma_{\mathrm{Ring13,ld}}=0.54$\,au and $\Sigma_{\circ,\mathrm{Ring13,ld}}=3\times10^{13}$. For Ring24 we used the same profile of the gas, but with the difference that, in an effort to recreate the break seen in the outer ring, we chose different values for $\gamma$ = -5 and $R_c$ = 38\,au between 28.6 and 35.6\,au. The surface density of the outer ring of large grains dust is thus given by
\begin{equation}
    \Sigma_{\mathrm{Ring24,ld}} = \Sigma_{\mathrm{c}} \left(\frac{r}{R_{\mathrm{c}}}\right)^{-\gamma} \exp\left[-\left(\frac{r}{R_{\mathrm{c}}}\right)^{2-\gamma}\right]\,\delta_{\mathrm{ld}}(r),
\end{equation}
where
\begin{equation}
  \delta_{\mathrm{ld}}(r) =
  \begin{cases}
  0                 & r < 24.6\text{\,au} \\
  6.24 \times10^{4} & 24.6 < r < 28.6\text{\,au} \\
  2.78 \times10^{4} & 28.6 < r < 37\text{\,au} \\
  2.14 \times10^{5} & 37   < r < 64\text{\,au.} \\
  \end{cases}
\end{equation}
Then the final density of large dust can be calculated as
\begin{equation}
\rho_{\mathrm{large-dust}}(r,z)=
\frac{\Sigma_{\mathrm{ld}}(r)}{\sqrt{2\pi} \, H(r)} \mathrm{exp}\left[-\frac{1}{2} \left(\frac{z}{H(r)}\right)^2\right] \, f_{\mathrm{ld}} \: \zeta .
\end{equation}

The two different populations of dust grains correspond to small grains, with radii ranging from 0.4 to 1.5\,$\micron$, and large dust grains, with radii from 0.4\,$\micron$ to 10\,mm. We computed the dust opacities using the {\tt bhmie} code provided in the \textsc{radmc3d} package, with a mix composed of 60\% silicate, 20\% graphite and 20\% ice.

@@

The simulated DPI image at 1.65\,$\micron$ in Fig.~\ref{fig:images_vs_simulated} was obtained with the scattering matrix calculated by the {\tt makeopac.py} script provided in the \textsc{radmc3d} package. As a way of reproducing the \textit{H}-band image, we used a different grain size distribution, where we used a Gaussian distribution centred at 0.4\,$\micron$ but  smeared out by 30\%, and with 20 grain size bins within that range. This distribution applies only to generate the NIR $Q_\phi$ image. To produce this $Q_\phi$ image we performed a linear combination of the two orthogonal linear polarizations \textit{U} and \textit{Q}, following \citet{Avenhaus_2017}, which gives a representation of an unbiased estimate of the polarized intensity image.

\begin{figure}
	\includegraphics[width=\columnwidth]{allprofiles.png}
        \caption{{\bf Top:} surface density profiles for the gas, the large and small grain populations. {\bf Bottom:} Aspect ratio profile $h(r)= H(r)/r$. The dashed lines crossing both panels correspond to transition radii in the parametric model.}
    \label{fig:profiles}
\end{figure}

The inner radius of the model grid was set to 0.1\,au,  and the outer radius of 100\,au, which is large enough for the dust disc to become undetectable. We set the values of the inclination an disc  position angle as the same as those obtained from the ALMA observation in Section~\ref{sec:Observations}, so the model has an inclination of i = 32.96\,$\degr$ and a P.A. = 77.31\,$\degr$. Finally, the distance is set at d = 72.4\,pc \citep{Gaia}.

>>>>

% Only include extra packages if you really need them. Common packages are:
\usepackage{graphicx}	% Including figure files
\usepackage{amsmath}	% Advanced maths commands
%% \usepackage{amssymb}	% Extra maths symbols
\usepackage{soul}
\usepackage{xcolor}  
\newcommand{\phil}[1]{\colorbox{yellow}{\bf #1}}

@@

% Abstract of the paper
\begin{abstract}
  The nearby V4046\,Sgr spectroscopic binary hosts a gas-rich disc known for its wide cavity and dusty ring.  We present high resolution ($\sim$20--50\,mas) ALMA observations of the 1.3\,mm  continuum which, combined with SPHERE-IRDIS polarized images and a well-sampled spectral energy distribution (SED), allow us to propose a physical model for the source using radiative transfer (RT) predictions. The new ALMA data reveal a very thin ring at a radius of 13.32$\pm$0.26\,au (Ring13), with a marginally resolved radial width of 1.50$\pm$0.72\,au. Ring13 is surrounded by a $\sim$10\,au-wide gap, and it is flanked by a very mm-bright outer ring (Ring24) with a sharp inner edge at 24\,au. The steeply decreasing brightness of Ring24 breaks at $\sim$35\,au into a shallow tail. In order to reproduce the SED, the model that we propose requires an inner ring at $\sim$6\,au (Ring6) \st{in} \phil{composed of} small dust grains, hiding under the IRDIS coronagraph, and \st{that surrounds} \phil{surrounding} an inner circumbinary disc. Faint mm-continuum close ($\sim0\farcs02 $ ****GIVE ERRORS***) to the stellar position is picked up by ALMA. The surprisingly thin Ring13 is nonetheless roughly 5 times wider than the model scale height, and could thus be long-lived. The strong near-far disc asymmetry at 1.65\,$\micron$ points at a very forward-scattering phase function, and requires grain radii of no less than 0.4\,$\micron$. The previously reported scattered-light shadow of the secondary star is also reproduced by the RADMC3D RT package. 
\end{abstract}

@@

V4046\,Sgr was observed in differential polarization imaging (DPI) mode with \st{SPHERE/IRDIS} \phil{SPHERE-IRDIS [for consistency]} on March 13, 2016 \citep[see][for details]{Avenhaus_2018}. Here we use a new reduction of the $H$ band data produced with the IRDAP pipeline \citep{2020A&A...633A..64V}, which can separate stellar and instrumental polarization. The polarized signal is consistent with the previous image in \citet{Avenhaus_2018}. The degree of linear polarization of the central and unresolved signal in V4046\,Sgr is only 0.13\%, with a systematic uncertainty of 0.05\% due to time-varying atmospheric conditions during the exposures. The angle of polarization is aligned with the disc major axis, as expected given that the target has Av=0.0 \citep{2016ApJ...828...69M} and the entire polarization is dominated by circumstellar rather than inter-stellar material.

@@

The resulting {\tt uvmem} image shown in \phil{the top right panel of} Fig.~\ref{fig:images_vs_simulated} exhibits previously unseen substructure of the disc. This image reveals that the disc features two rings of large dust grains with a broad gap between them, i.e. Ring13 at 13\,au and Ring24 starting at 24\,au. The wide and bright Ring24 reaches its peak intensity at $\sim$30\,au, beyond which it drops steeply before breaking at $\sim$35\,au into a shallow tail. While this is the first observation of Ring13, \citet{Ru_z_Rodr_guez_2019} did anticipate its existence as their ALMA continuum image showed a distinct excess between $\sim$10 and 17\,au.

\begin{figure*}
  \includegraphics[width=\textwidth]{hot_two_E.pdf}
  \caption{Comparison of observations \phil{(top)} and simulated images \phil{(bottom)} at 1.65\,$\micron$ \phil{(left)} and 1.3 mm continuum \phil{(right)} of the circumbinary disc orbiting V4046\,Sgr. \st{From top to bottom: DPI image and ALMA Band 6 observations; simulated images of the parametric model.} \phil{\textit{Top left panel:}} SPHERE-IRDIS \textit{H}-band image with a yellow filled circle that represents the N\_ALC\_YJH\_S coronagraph with a radius of $\sim0\farcs12$, or $\sim$8.6\,au at 72.4\,pc. \phil{\textit{Top right panel:}} 1.3\,mm continuum {\tt uvmem} model image. The yellow ellipse shows the size of the natural-weighted beam ($ 0\farcs062 \, \times \, 0\farcs055$), and the small orange ellipse shows an estimated {\tt uvmem} beam size ($\sim0\farcs035 \, \times \, \sim0\farcs031$). The inset zooms into the central emission, and the green star marks the \st{star positions} \phil{binary position}. \phil{\textit{Bottom left panel:}} synthetic image at 1.65\,$\upmu$\phil{m}. \phil{\textit{Bottom right panel:}} synthetic image at 1.3\,mm. . For all the images in the figure the colour scale is linear.}
  \label{fig:images_vs_simulated}
\end{figure*}

@@

Interestingly, the ALMA image also detects faint 1.3\,mm continuum emission near the stellar positions (See the inset in Fig.~\ref{fig:images_vs_simulated}). Since this faint central emission is larger than the angular resolution, it is probably stemming from thermal emission from  large dust grains rather directly from the stars. The main blob of this dust structure is at a estimate distance of only $0\farcs012\pm0\farcs002$, or $\sim$0.9\,au from the binary system, and may be part of \phil{an} inner disc introduced in the RT model to match the SED (see Sec.~\ref{sec:model} below).

@@

The scattered-light image \st{shown} in \phil{the top left panel of} Fig.~\ref{fig:images_vs_simulated} also shows a double ring structure in the micron-sized dust distribution. The observed morphology presents an inner cavity of $\sim$10\,au in radius and two rings located at 14.10$\pm$0.01, coincident with Ring13, and 24.62$\pm$0.08\,au, coincident with Ring24, with a small gap between them at $\sim$20\,au. The observed second ring matches the inner wall of the 1.3\,mm continuum emission outer ring \citep{Ru_z_Rodr_guez_2019}. Two other important features that are present in the image are: the brightness asymmetry and the shadows projected on the disc produced by the close binary system as they eclipse each other, discovered by \citet{dOrazi}.

@@

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{SED_.png}
    \caption{\phil{Change labels in legend: binary instead of stars, RT Model} \phil{Spectroscopy Data, Photometry Data.} The observed SED of V4046\,Sgr (black points and solid red curve) compared with the model (blue). The black points represent the measured photometry and the red line shows an archival \textit{Spitzer} IRS spectrum. The dashed silver curve shows the emission of the stellar photosphere model.}
    \label{fig:SED}
\end{figure}

@@

The stars were modeled using two Kurucz photospheres models \citep{1979ApJS...40....1K, 1997A&A...318..841C}, with T$_{\mathrm{eff},1} =$ 4350\,K, R$_{*,1} =$ 1.064\,R$_{\sun}$, M$_{*,1} =$ 0.90\,M$_{\sun}$ and T$_{\mathrm{eff},2} =$ 4060\,K, R$_{*,2} =$ 1.033\,R$_{\sun}$, M$_{*,2} =$ 0.85\,M$_{\sun}$ respectively and with an accretion rate of \st{$\mathrm{log}(\,\dot{\mathrm{M}/(\mathrm{M}_{\sun}\,\mathrm{yr^{-1}})}) = -$9.3} \phil{[replace by:]} $\mathrm{log}(\,\dot{\mathrm{M}}/(\mathrm{M}_{\sun}\,\mathrm{yr^{-1}})) = -$9.3 for both cases to include excess UV due to stellar accretion \citep{10.1111/j.1365-2966.2011.19366.x}. The stars were placed at a mutual separation of 0.041\,au, so that their centre of mass coincides with the origin, and oriented at a PA of 250\,$\degr$, so that the secondary lies to the NWW from the primary, thus casting the same shadow as observed by \citet{dOrazi}.

Reproducing the radial and vertical structure of the V4046\,Sgr disc turned out to be challenging. We built the model in terms of the gas distribution, and with two different dust populations: larger grains that are vertically settled and dominate the total dust mass, and a population of smaller grains that are uniformly mixed with the gas and reach \phil{higher regions} \st{larger heights} above the mid-plane.

Assuming a three dimensional model in a cylindrical reference frame with coordinates ($r$, $\theta$, $z$) \phil{[just for conventional reasons, I would use $\phi$ instead of $\theta$]}, the gas density ($\rho_{\mathrm{gas}}$) distribution follows
\begin{equation}
  \rho_{\mathrm{gas}}(r,z) =\frac{\Sigma_{\mathrm{gas}}(r)}{\sqrt{2\pi} \, H(r)} \mathrm{exp}\left[-\frac{1}{2} \left(\frac{z}{H(r)}\right)^2\right],
\end{equation}
where $H(r)$ is the scale height profile and $\Sigma_{\mathrm{gas}}(r)$ is the gas surface density profile.

The parametric scale height profiles for the gas and for each dust population are 
\begin{equation}
    \label{scale}
  H(r)=\chi \, H_{\circ} \, [r/r_{\circ}]^{\psi(r)},
\end{equation}
where $H_\circ$ is the scale height at \st{r} \phil{$r$}= $r_\circ$, $\psi$ is the flaring index and $\chi$ is a scaling factor (in the range $0-1$) that mimics dust settling. The gas and the small dust \phil{(sd)} grains have no settling, so \st{$\chi_{gas}$} \phil{$\chi_{\rm gas}$ = $\chi_{\rm sd}$} = 1. The radial spread of Ring13 appears about five times wider in the gas-tracing NIR observations than in the fluxes received from larger grains with ALMA. We assume that the same ratio holds in the vertical direction (due to the settling of larger grains towards the disk's midplane), leading to \st{$\chi_{ld}=1/5$} \phil{$\chi_{\rm ld}=0.2$ [adapt this in case you changed the model to 0.3]}.

For the \st{vertical structure} \phil{scattering surfaces}, \citet{dOrazi} found flaring angles of $\varphi$ = 6.2$\pm$0.6\,$\degr$ for the inner ring and $\varphi$ = 8.5$\pm$1.0\,$\degr$ for the outer one. Our model uses the same values, with two different flaring \st{indexes} \phil{indices, $\psi_1$ and $\psi_2$} \st{$\psi$}. The separation between the two values were set at $r$ = 18\,au with \phil{$\psi_1=0.15$} for Ring6 and Ring13, and \phil{$\psi_2=0.5$} for Ring24. The scale height is $H_\circ = 0.45$\,au at $r_\circ = 18$\,au.

We propose a three ringed structure \phil{to reproduce the observations.} \phil{We separate the disk into four individual regions:}\st{, so we defined the total gas surface density by a combination of four individual components:} the inner disc, Ring6, Ring13 and Ring24. The \st{total} \phil{combined} gas surface density \phil{profile} is then  given  by:
\begin{equation}
  \Sigma_{\mathrm{gas}}(r) = \Sigma_{\mathrm{inner\,disc}} + \Sigma_{\mathrm{Ring6}} + \Sigma_{\mathrm{Ring13}} + \Sigma_{\mathrm{Ring24}}
\end{equation}

The inner disc follows a power law function defined by
\begin{equation}
  \Sigma_{\mathrm{inner\,disc}}(r) =\Sigma_\mathrm{c} \left(\frac{r}{R_\mathrm{c}}\right)^{-\gamma}  \, \mathrm{exp}\left[-\left(\frac{r}{R_\mathrm{c}}\right)^{2-\gamma}\right],
\end{equation}
where $R_c$ is a characteristic radius and $\gamma$ is the surface density \st{gradient} \phil{power-law index}. We used $R_c$ = 16\,au, $\Sigma_\mathrm{c} =2.7\times10^{-4}$\phil{\,$\mathrm{g\,cm^{-3}}$} and a fixed $\gamma$ = 1 as it is a typical value for discs \citep{Andrews_2009,Andrews_2010}. \st{The gas surface density begin at 0.3\,au, out of the zone expected to be cleared by dynamical interactions with the central binary} \citep{Art_Lu}, \st{which is expected to be $\sim$0.2\,au.} \phil{Our model extends from 0.3\,au outwards, as the interior is expected to be} \phil{cleared by dynamical effects of the central binary} \citep{Art_Lu}.

We \st{chose} \phil{choose} to use Gaussian profiles to parameterize Ring6 and Ring13,
\begin{equation}
  \Sigma_{\mathrm{Ring}}(r) = \frac{\Sigma_\circ}{\sqrt{2 \pi} \sigma}
  \, \mathrm{exp}\left[-\frac{1}{2}\left(\frac{r-\mu}{\sigma}\right)^{2}\right],
\end{equation}
where we define constants that correspond to the centroid radii \{$\mu_{\mathrm{Ring6}}=5.5$\,au, $\mu_{\mathrm{Ring13}}=15$\,au\}, ring widths \{$\sigma_{\mathrm{Ring6}}=1$\,au, $\sigma_{\mathrm{Ring13}}=2.05$\,au\}, and normalizations \phil{[this $\Sigma$ cant be right? Also, units for density!]} \{ $\Sigma_{\circ,\mathrm{Ring6}}=8\times10^{12}$, $\Sigma_{\circ,\mathrm{Ring13}}=4.2\times10^{13}$\} for both components separately.

For Ring24 we used the same power law \st{than} \phil{as for} the inner disc but scaled by \st{a $\delta_{\mathrm{sd}}$ factor} \phil{an empirically obtained factor, $\delta_{\mathrm{sd}}$= 5.3$\times 10^4$}:
\begin{equation}
  \Sigma_{\mathrm{Ring24}} = \Sigma_{\mathrm{inner\,disc}}(r)\, \delta_{\mathrm{sd}},
\end{equation}
\st{with $\delta_{\mathrm{sd}}$ = 5.3$\times 10^4$.} \st{But the inner wall} \phil{The inner edge} of Ring24 follows a different \st{behaviour} \phil{profile}. Between $R_\mathrm{in}$ and $R_\mathrm{peak}$, which respectively mark  the \st{beginning} \phil{inner edge} and the \phil{location of} maximum density \st{peak} of the outer ring, the gas density profile is multiplied by an additional factor
\begin{equation}
    \epsilon(r) = \left(\frac{ r - R_\mathrm{in}}{R_\mathrm{peak} - R_\mathrm{in}}\right)^3.
\end{equation}
This parameter \st{allow} \phil{allows} us to model a smoother inner \st{wall} \phil{edge} of the outer ring, with $R_\mathrm{in,gas}$ = \st{18.\,au} \phil{18.0\,au} and $R_\mathrm{peak,gas}$ = 26.8\,au. This factor is also applied to the large dust population with $R_\mathrm{in,ld}$ = 24.7\,au and $R_\mathrm{peak,ld} = R_\mathrm{peak,gas}$.

@@

Since the large dust grains are less coupled to the gas, their distribution has some important differences that require a special parameterisation, with a large inner cavity, a larger gap between the rings and a break in the outer ring. We also truncated the \st{model large-grain density} \phil{profile of large dust grains} at 64\,au. \st{The large-dust surface density profile is} \phil{It is then} defined by the sum of its two components
\begin{equation}
  \Sigma_{\mathrm{ld}}(r) = 
  \Sigma_{\mathrm{Ring13,ld}} + \Sigma_{\mathrm{Ring24,ld}}.
\end{equation}

For the inner ring, we \st{chose} \phil{choose} a Gaussian profile parameterized with centroid radius $\mu_{\mathrm{Ring13, ld}}=13.38$\,au, ring width of $\sigma_{\mathrm{Ring13,ld}}=0.54$\,au and $\Sigma_{\circ,\mathrm{Ring13,ld}}=3\times10^{13}$. For Ring24 we used the same profile \st{of} \phil{as for} the gas, but with the difference that, in an effort to recreate the break seen in the outer ring, we \st{chose} \phil{choose} different values for \st{$\gamma$ = -5} \phil{$\gamma = -5$} and $R_c$ = 38\,au between 28.6 and 35.6\,au. The surface density \st{of the outer ring of large grains dust} \phil{for large dust grains in the outer ring} is thus given by
\begin{equation}
    \Sigma_{\mathrm{Ring24,ld}} = \Sigma_{\mathrm{c}} \left(\frac{r}{R_{\mathrm{c}}}\right)^{-\gamma} \exp\left[-\left(\frac{r}{R_{\mathrm{c}}}\right)^{2-\gamma}\right]\,\delta_{\mathrm{ld}}(r),
\end{equation}
where
\begin{equation}
  \delta_{\mathrm{ld}}(r) =
  \begin{cases}
  0                 & r < 24.6\text{\,au} \\
  6.24 \times10^{4} & 24.6 < r < 28.6\text{\,au} \\
  2.78 \times10^{4} & 28.6 < r < 37\text{\,au} \\
  2 .14 \times10^{5} & 37   < r < 64\text{\,au.} \\
  \end{cases}
\end{equation}
Then the final density of large dust can be calculated as
\begin{equation}
\rho_{\mathrm{large-dust}}(r,z)=
\frac{\Sigma_{\mathrm{ld}}(r)}{\sqrt{2\pi} \, H(r)} \mathrm{exp}\left[-\frac{1}{2} \left(\frac{z}{H(r)}\right)^2\right] \, f_{\mathrm{ld}} \: \zeta .
\end{equation}

The two different populations of dust grains correspond to small grains, with radii ranging from 0.4\phil{\,$\micron$} to 1.5\,$\micron$, and large dust grains, with radii from 0.4\,$\micron$ to 10\,mm. We computed the dust opacities using the {\tt bhmie} code provided in the \textsc{radmc3d} package, with a mix composed of 60\% silicate, 20\% graphite and 20\% ice.

@@

The simulated DPI image at 1.65\,$\micron$ in Fig.~\ref{fig:images_vs_simulated} was obtained with the scattering matrix calculated by the {\tt makeopac.py} script provided in the \textsc{radmc3d} package. As a way of reproducing the \textit{H}-band image, we used a different grain size distribution, where we \st{used} \phil{centred} a Gaussian \st{distribution} \st{centred} at 0.4\,$\micron$ \st{but} \phil{,}  smeared out by 30\%, and \phil{distributed over 20 bins within that range} \st{with 20 grain size bins within that range}. This distribution applies only to generate the NIR $Q_\phi$ image. To produce this $Q_\phi$ image we performed a linear combination of the two orthogonal linear polarizations \textit{U} and \textit{Q}, following \citet{Avenhaus_2017}, which gives a representation of an unbiased estimate of the polarized intensity image.

\begin{figure}
	\includegraphics[width=\columnwidth]{allprofiles.png}
        \caption{{\bf Top:} surface density profiles for \st{the} gas, \st{the}large and small \phil{dust grains} \st{grain populations}. {\bf Bottom:} Aspect ratio profile $h(r)= H(r)/r$. The \st{dashed} \phil{dotted} lines crossing both panels correspond to transition radii in the parametric model.}
    \label{fig:profiles}
\end{figure}

The inner radius of the model grid was set to 0.1\,au,  and the outer radius \st{of} \phil{to} 100\,au, which is large enough for the dust disc to \st{become} \phil{be} undetectable. We set the values of the inclination \st{an} \phil{and} disc position angle \phil{to} \st{as} the same as \st{those} obtained from the ALMA observation in Section~\ref{sec:Observations}, \st{so} \phil{such that} the model has an inclination of i = 32.96\,$\degr$ and a P.A. = 77.31\,$\degr$. Finally, the distance is set \st{at} \phil{to} d = 72.4\,pc \citep{Gaia}.
